Modelling report

### 2024-10-19 notebooks/02-modelling.qmd

---
title: Modelling report
subtitle: "Are there unconscious visual images in aphantasia? Development of an implicit priming paradigm"
# setting for proper numbering of sections
crossref: 
  chapters: true
  custom:
    - kind: float
      key: suppfig
      reference-prefix: Figure S
      space-before-numbering: false
    - kind: float
      key: supptbl
      reference-prefix: Table S
      space-before-numbering: false
supptbl-cap-location: top
---

>>>>

---
title: Modelling report
subtitle: "Are there unconscious visual images in aphantasia? Development of an implicit priming paradigm"
# setting for proper numbering of sections
crossref: 
  chapters: true
  custom:
    - kind: float
      key: suppfig
      reference-prefix: Figure S
      space-before-numbering: false
    - kind: float
      key: supptbl
      reference-prefix: Table S
      space-before-numbering: false
supptbl-cap-location: top
format: html
---
